Title Goes Here

### 2020-02-25 paper/paper.tex
Made 'todo' environment

@@

\subsection{Translation Example}
\begin{tcolorbox}
  \textbf{TODO}: Does it make sense for this to be a subsection of the intro?
\end{tcolorbox}

@@

\begin{tcolorbox}
  \textbf{TODO}: Should we use a single nested pattern match in the above block? Both
  are functional (and equivalent) from a technical perspective.
\end{tcolorbox}

@@

\begin{tcolorbox}
  \textbf{TODO}: Should we make a synonym for this constraint since it is used in
multiple places? Like this:
\begin{lstlisting}
type CanonicalIsIdem t =
  ERepTy (ERepTy t) ~ ERepTy t
\end{lstlisting}
\end{tcolorbox}

@@

\subsection{Connection to Church encodings}
\begin{tcolorbox}
  \textbf{TODO}: Write this subsection
\end{tcolorbox}

@@

\section{Representing tail recursion}
\begin{tcolorbox}
  \textbf{TODO}: Expand the explanation in this section
\end{tcolorbox}

@@

\clearpage
\subsection{Syntactic Transformations of the Core Plugin}
\begin{tcolorbox}
  \textbf{TODO}: Should we use Oxford brackets here? Maybe a bit unusual, but we are operating syntactically and mapping from \ttt{a} to \ttt{E a} (could \ttt{E a} be considered an "intermediary" semantic domain?).
\end{tcolorbox}
\vspace*{-0.6cm}
\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &\rewrites \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}
\end{align*}

@@

\begin{tcolorbox}
  \textbf{TODO}: Fill in
\end{tcolorbox}

>>>>

\newenvironment{todo}
  {\begin{tcolorbox}
   \textbf{TODO}:
  }
  {\end{tcolorbox}
  }

@@

\subsection{Translation Example}
\begin{todo}
  Does it make sense for this to be a subsection of the intro?
\end{todo}

@@

\begin{todo}
  Should we use a single nested pattern match in the above block? Both
  are functional (and equivalent) from a technical perspective.
\end{todo}

@@

\begin{todo}
  Should we make a synonym for this constraint since it is used in
multiple places? Like this:
\begin{lstlisting}
type CanonicalIsIdem t =
  ERepTy (ERepTy t) ~ ERepTy t
\end{lstlisting}
\end{todo}

@@

\subsection{Connection to Church encodings}
\begin{todo}
  Write this subsection
\end{todo}

@@

\section{Representing tail recursion}
\begin{todo}
  Expand the explanation in this section
\end{todo}

@@

\clearpage
\subsection{Syntactic Transformations of the Core Plugin}
\begin{todo}
  Should we use Oxford brackets here? Maybe a bit unusual, but we are operating syntactically and mapping from \ttt{a} to \ttt{E a} (could \ttt{E a} be considered an "intermediary" semantic domain?).
\end{todo}
\vspace*{-0.6cm}
\begin{align*}
  D&\expr{\ttt{f x = internalize (externalize (case s of \{ ... \}))}}\\
      &\rewrites \begin{cases}
        \ttt{f = internalize $C^{*}\expr{\ttt{externalize (runIter ($\lambda \ttt{x} \rarr \ttt{case s of $T'_{\ttt{f}}\expr{\ttt{\{ ... \}}}$}$))}}$} & \text{if \ttt{f} occurs free in \ttt{\{ ... \}}}\\
        \ttt{f x = internalize $C^{*}\expr{\ttt{externalize (case s of \{ ... \})}}$} & \text{otherwise}
      \end{cases}
\end{align*}

@@

\begin{todo}
  Fill in
\end{todo}
